### 2009-03-25 doc/storage_system/arc-storage-manual.tex
manual about ARC DMC

@@

>>>>

This version of the \verb!arc_storage_cli! tool currently does not support recursive methods or working with multiple files at once.

@@

\section{Using the ARC DMC} % (fold)
\label{sec:using_the_arc_dmc}

ARC has its own multi-protocol storage client tools which provide a unified way to access different kind of storage. For all the supported types there is a DMC module. We created a DMC module for the ARC storage as well. If it is compiled and installed, then you can use the \verb!arcls!, \verb!arccp!, \verb!arcrm!, etc. tools with the \verb!arc://! protocol to access the ARC storage system. You need to have a Bartender URL configured in the \verb!client.xml! user config.

\begin{verbatim}
$ arcls arc:///
$ arccp orange arc:///orange
$ arcls arc:///
orange
$ arccp arc:///orange /tmp/orange
$ cat /tmp/orange 
orange
$ arcrm arc:///orange
$ arcls arc:///
$ 
\end{verbatim}

TODO: if Bartender returns a ByteIO URL - not good, need to fix it.
